### 2016-09-30 simplification.tex
reviewer 1 point 2 (Carette's citation replaced)
Don't use longtable for the simplification table
It should only be used for tables that can't fit on one page.

The generic way to simplify an expression is by calling the \texttt{simplify}
function.
It must be emphasized that simplification is not a rigorously defined
mathematical operation~\cite{Carette2004understanding}.
The \texttt{simplify} function applies several simplification routines along
with heuristics to make the output expression ``simple''.\footnote{The
\texttt{measure} parameter of the \texttt{simplify}
function lets the user specify the Python function used to determine how complex an
expression is.  The default measure function returns the total number of
operations in the expression.}

@@

\begin{longtable}[htbc]{lp{0.83\linewidth}}
\caption{Some SymPy Simplification Functions\label{simplify-table}}\\
\toprule
\verb|expand| & expand the expression \\
\verb|factor| & factor a polynomial into irreducibles \\
\verb|collect| & collect polynomial coefficients \\
\verb|cancel| & rewrite a rational function as $p/q$ with common factors
canceled \\
\verb|apart| & compute the partial fraction decomposition of a rational function
\\
\verb|trigsimp| & simplify trigonometric expressions~\cite{fu2006automated} \\
\verb|hyperexpand| & expand hypergeometric functions~\cite{Roach1996hyper,roach1997meijerg} \\
\bottomrule
\end{longtable}

>>>>

The generic way to simplify an expression is by calling the \texttt{simplify}
function.
It must be emphasized that simplification is not a rigorously defined
mathematical operation~\cite{Moses1971simplification}.
The \texttt{simplify} function applies several simplification routines along
with heuristics to make the output expression ``simple''.\footnote{The
\texttt{measure} parameter of the \texttt{simplify}
function lets the user specify the Python function used to determine how complex an
expression is.  The default measure function returns the total number of
operations in the expression.}

@@

\begin{center}
\begin{table}[htbc]
\caption{Some SymPy Simplification Functions}\label{simplify-table}
\begin{tabular}{lp{0.83\linewidth}}
\toprule
\verb|expand| & expand the expression \\
\verb|factor| & factor a polynomial into irreducibles \\
\verb|collect| & collect polynomial coefficients \\
\verb|cancel| & rewrite a rational function as $p/q$ with common factors
canceled \\
\verb|apart| & compute the partial fraction decomposition of a rational function
\\
\verb|trigsimp| & simplify trigonometric expressions~\cite{fu2006automated} \\
\verb|hyperexpand| & expand hypergeometric functions~\cite{Roach1996hyper,roach1997meijerg} \\
\bottomrule
\end{tabular}
\end{table}
\end{center}
